---
title: "Regression Models Motor Trend Analysis"
author: "Qiang Wu"
date: "December 12, 2015"
output: pdf_document
---

1. load data mtcars

```{r, echo=TRUE, cache=TRUE}
library(ggplot2)
data("mtcars")
summary(mtcars)
```

2. First let's plot the mpg vs the auto/manual
```{r, echo=TRUE, cache=TRUE}
ggplot(mtcars, aes(factor(am), mpg)) + geom_boxplot()
```

3. From the plot, we can clearly see there is mpg difference between mpg in auto and manual cars
```{r, echo=TRUE, cache=TRUE}
median(mtcars[mtcars$am==0,]$mpg)
median(mtcars[mtcars$am==1,]$mpg)
```

4. Try to run regression.
```{r, echo=TRUE, cache=TRUE}
fit<-lm(mpg~factor(am), mtcars)
summary(fit)
```

5. From fit, we can see there is 
`r coef(fit)[2]` difference between auto/manual cars.
It's also greater than 2 * `r coef(summary(fit))[4]`
And p value is very small, so this means this slop is significant.

6. play with mtcars more, if we consider all information
```{r, echo=TRUE, cache=TRUE}
summary(lm(mpg~., mtcars))
```
We can see no parameter is significant any more. But seems weight (wt) is more important than others.

7. If we think about am and wt only.
```{r, echo=TRUE, cache=TRUE}
summary(lm(mpg~factor(am)+wt, mtcars))
```
We can see in this case, am is not as importatn as weight.

